Lynott et al. (2014) - Potential error in statistics reporting

### 2017-11-13 manuscript.Rmd
fixed weird "HEAD" insertions from earlier merge conflict; changed example 1 to report means and SDs from replication study rather than original

```{r include = FALSE}
source("NSEQ_Brandt_Example.R")

@@

@Banerjee2012 reported that `r orig.N` participants who had been asked to describe an unethical deed from their past judged the room to be darker than participants who had been asked to describe an ethical deed ($M_{unethical}= `r orig.m1`$, ${SD}_{unethical}= `r orig.sd1`$, $M_{ethical}=`r orig.m2`$, ${SD}_{ethical}=`r orig.sd2`$, $t(`r orig.df`)= `r orig.t`$, $p= `r printp(orig.p)`$, $d= `r printnum(orig.d)`$). A close replication by @Brandt2014 with `r rep.n1+rep.n2` participants found no significant effect ($t(`r printnum(rep.df)`)=`r printnum(rep.t)`$, $p=`r printp(rep.p)`$, $d=`r printnum(rep.d)`$). Following the small telescopes approach, we can calculate the effect size the original study had 33% power to detect --- $d = `r printnum(d.33)`$ --- and use this as our SESOI. If we run a TOST with Welch's *t*-test for independent samples and equivalence bounds of ${\Delta}_L=`r printnum(-d.33)`$ and ${\Delta}_U=`r printnum(d.33)`$, we indeed find that the effect reported by the replication study is statistically equivalent, $t(`r printnum(Brandt$TOST_df)`)=`r printnum(min(Brandt$TOST_t1, Brandt$TOST_t2))`$, $p=`r printp(max(Brandt$TOST_p1, Brandt$TOST_p2))`$ (Figure 2A).

@@

```{r, include=FALSE}
source("SEQ_Hyde_Example.R")
```

@@

## Example 3: Not Statistically Equivalent and Not Statistically Different
```{r include=FALSE}
source("NSNEQ_Moon_Example.R")
```

@@

## Example 4: Statistically Inferior and Not Statistically Different
```{r include=FALSE}
source("NSEQ_Lynott_example.R")
```

@@

In this case, it is not immediately clear what an objective criterion for the sESOI would be. However, as this is a replication, we could decide that we do not care about an effect if the difference is smaller than the smallest effect that the original study could potentially detect. This means that we will use the critical z value (~1.96 in a two-tailed test with an alpha of 0.05) as our bounds ($\Delta = \pm `r printnum(qnorm(1-0.05/2))`$). To figure out what difference corresponds to a critical z in the original study, we multiply critical z with the standard error.

@@

## Example 5: Statistically Equivalent and not Statistically Different
```{r include = FALSE}
source("corr_Kahane_Example.R")
```

>>>>

```{r include = FALSE}
source("Example1_Brandt-et-al_study1.R")

@@

@Banerjee2012 reported that `r orig.N` participants who had been asked to describe an unethical deed from their past judged the room to be darker than participants who had been asked to describe an ethical deed ($t(`r orig.df`)= `r orig.t`$, $p= `r printp(orig.p)`$, $d= `r printnum(orig.d)`$). A close replication by @Brandt2014 with `r rep.n1+rep.n2` participants found no significant effect ($M_{unethical}= `r rep.m1`$, ${SD}_{unethical}= `r rep.sd1`$, $M_{ethical}=`r rep.m2`$, ${SD}_{ethical}=`r rep.sd2`$, $t(`r printnum(rep.df)`)=`r printnum(rep.t)`$, $p=`r printp(rep.p)`$, $d=`r printnum(rep.d)`$). Following the small telescopes approach, we can calculate the effect size the original study had 33% power to detect --- $d = `r printnum(d.33)`$ --- and use this as our SESOI. If we run a TOST with Welch's *t*-test for independent samples and equivalence bounds of ${\Delta}_L=`r printnum(-d.33)`$ and ${\Delta}_U=`r printnum(d.33)`$, we indeed find that the effect reported by the replication study is statistically equivalent, $t(`r printnum(Brandt$TOST_df)`)=`r printnum(min(Brandt$TOST_t1, Brandt$TOST_t2))`$, $p=`r printp(max(Brandt$TOST_p1, Brandt$TOST_p2))`$ (Figure 2A).

@@

```{r, include=FALSE}
source("Example2_Hyde-et-al.R")
```

@@

## Example 3: Not Statistically Equivalent and Not Statistically Different
```{r include=FALSE}
source("Example3_MoonRoeder.R")
```

@@

## Example 4: Statistically Inferior and Not Statistically Different
```{r include=FALSE}
source("Example4_Lynott-et-al.R")
```

@@

In this case, it is not immediately clear what an objective criterion for the sESOI would be. However, as this is a replication, we could decide that we do not care about an effect if the difference is smaller than the smallest effect that the original study could potentially detect. This means that we will use the critical z value (~1.96 in a two-tailed test with an alpha of 0.05) as our bound ($\Delta = \pm `r printnum(qnorm(1-0.05/2))`$). To figure out what difference corresponds to a critical z in the original study, we multiply critical z with the standard error.

@@

## Example 5: Statistically Equivalent and not Statistically Different
```{r include = FALSE}
source("Example5_Kahane-et-al-study4.R")
```
